\T{The Beginning}
\C In the beginning God created the heavens and the earth. \V Now the earth was
formless and empty, darkness was over the surface of the deep, and the Spirit of
God was hovering over the waters.

\V And God said, "Let there be light," and there was light. \V God saw that the
light was goog, and he separated the light from the darknes. \V God called the
light "day," and the darkness he called "night." And there was evening, and
there was morning -- the first day.

\V And God said, "Let there be an expanse between the waters to separate water
from water". \V So God made the expanse and separated the water under the
expanse from the water above it. And it was so. \V God called the "sky." And
there was evening, and there was morning -- the second day.

\V And God sai, "Let the water under the sky be gathered to one place, and let
dry ground appear." And it was so. \V God called the dry ground "land," and the
gathered waters he called "seas." And God saw that it was good.

\V Then God said, "Let the land produce begetation: seed in it, according to
their various kinds." And it was so. \V The land produced vegetation: plants
bearing seed acoording to their kinds and trees bearing gruit with seed in it
according to their kinds. And God saw that it was good. \V And there was
evening, and there was moring -- the third day.

\V And God said, "Let there be lights in the expanse of the sky to separate the
day from the night, and let them serve as signs to mark seasons and days and
years, \V and let them be lights in the expanse of the sky to give light on the
earth." And it was so. \V God made two great lights -- the greater light to
govern the day and the lesser light to govern the night. He also made the stars.
\V God set them in the expanse of the sky to give light on the earth, \V to
govern th day and the night, and to separate light from darkness. And God saw
that it was good. \V And there was evening, and there was morning -- the fourth
day.

\V And God said, "Let the water teem with living creatures, and let birds fly
above the earth across the expanse of the sky." \V So God created the great
creatures of the sea and every living and moving thing with which the water
teems, acoording to their kinds, and every winged bird acoording to its kind.
And God saw that it was good. \V God blessed them and said, "Be fruitful and
increase in number and fill the water in the seas, and let the birds increase on
the earth." \V And there was evening, and there was morning -- the fifth day.

\V And God said, "Let the land produce living creatures acoording to their
kinds: livestock, creatures that move along the ground, and wild animals, each
according to its kind." And it was so. \V God made the wild animals according to
their kinds, the livestock acoording to their kinds, and all the creatures that
move along the ground acoording to their kinds. And God saw that it was good.

\V Then God said, "Let us make man in our image, in our likeness, and let them
rule over the fish of the sea and the birds of the air, over the livestock, over
all the earth, and over all the creatures that move along the ground."

\begin{quotation}
\V So God created man in his own image,\\
in the image of God he created him;\\
male and female he created them.
\end{quotation}

\V God blessed them and said to them, "Be fruitful and increase in number; fill
the earth and subdue it. Rule over the fish of the sea and birds of the air and
over every living creature tha moves on the ground."

\V Then God said, "I give you every ssed-bearing plant on the face of the whole
earth and every tree that has fruit with seed in it. Thy will be yours for food.
\V And to all the beasts of the earth and all the birds of the air and all the
creatures that move on the ground -- everything that has the breath of life in
it -- I give every green plant for food." And it was so.

\V God saw all that he had made, and it was very good. And there was evening,
and there was morning -- the sixth day.

\C Thus the heavens and the earth were completed in all their vast array.

\V By the seventh day God had finished the work he had been doing; so on the
seventh day he rested from all his work. \V And God blessed the sevent day and
made it holy, because on it he rested from all the work of creating that he had
done.
