\T{Adam and Eve}
\V This is the account of the heavens and the earth when they were created.

When the LORD God made the earth and the heavens -- \V and no shrub of the field
had yet appeared on the earth and no plant of the field had yet sprung up, for
the LORD God had not sent rain on the earth and there was no man to work the
ground, \V but streams came up from the earth and watered the whole surface of
the ground -- \V the LORD God formed the man from the dust of the ground and
breathed into his nostrils the breath of life, and the man became a living
being.

\V Now the LORD God had planted a garden in the east, in Eden; and there he put
the man he had formed. \V And the LORD God made all kings of trees grow out of
the ground -- trees that were pleasing to the eye and good for food. In the
middle of the garden were the tree of life and the tree of the knowledge of good
and evil.

\V A river watering the garden flowed from Eden; from there it was separated
into four headwaters. \V The name of the first is the Pishon; it winds through
the entire land of Havilah, where there is gold. \V (The gold of that land is
good; aromatic resin and onyx are also there.) \V The name of the second river
is the Gihon; it winds throught the entire land of Cush. \V The name of the
third river is the Tigris; it runs along the east side of Asshur. And the fourth
river is the Euphrates.

\V The LORD God took the man and put him in the Garden of Eden to work it and
take care of it. \V And the LORD God commanded the man, "Yout are free to eat
from any tree in the garden; \V gut you must not eat from the tree of the
knowledge of good and evil, for when you eat of it you will surely die."

\V The LORD God had formed out of the ground all the beasts of the field and all
the birds of the air. He brought them to the man to see what he would name them;
and whatever the man called each living creature, that was its name. \V So the
man gave names to all the livestock, the birds of the air and all the beasts of
the field.

\V But for Adam no suitable helper was found. \V So the LORD God caused the man
to fall into a deep sleep; and while he was sleeping, he took on of the man's
ribs and closed up the place with flesh. \V Then the LORD God made a woman from
the rib he had taken out of the man, and he brought her to the man.

\V The man said,

\begin{quotation}
"This is now bone of my bone\\
and flesh of my flesh;\\
she shall be called 'woman,'\\
for she was taken out of man."
\end{quotation}

\V For this reason a man will leave his father and mother and be united to his
wife, and they will become one flesh.

\V The man and his wife were both naked, and they felt no shame.
