\T{Cain and Abel}
\C Adam lay with his wife Eve, and she became pregnant and gave birth to Cain.
She said, "With the help of the LORD I have brought forth a man." \V Later she
gave birth to his brother Abel.

Now Abel kept flocks, and Cain worked the soil. \V In the course of time Cain
some of the fruits of the soil as an offering to the LORD. \V But Abel brought
fat portions from some of the firstborn of his flock. The LORD looked with favor
on Abel and his offering, \V but on Cain and his offering he did not look with
favor. So Cain was very angry, and his face was downcast.

\V Then the LORD said to Cain, "Why are you angry? Why is your face downcast? \V
If you do what is right, will you not be accepted? But if you do note do what is
right, sin is crouching at your door; it desires to have you, but you must
master it."

\V Now Cain said to his brother Abel, "Let's go out to the field." And while
they were in the field, Cain attacked his brother Abel and killed him.

\V Then the LORD said to Cain, "Where is your brother Abel?"

"I don't know," he replied. "Am I my brother's keeper?"

\V The LORD said, "What have you done? Listen! Your brother's blood cries out to
me from the ground. \V Now you are under a curse and driven from the ground,
which opened its mounth to receive your brother's blood from your hand. \V When
you work the ground, it will no longer yield its crops for you. You will be a
restless wanderer on the earth."

\V Cain said to the LORD, "My punishment is more than I can bear. \V Today you
are driving me from the land, and I will be hidden from your presence; I will be
a restless wanderer on the earth, and whoever finds me will kill me."

\V But the LORD said to him. "Not so; if anyone kills Cain, he will suffer
vengeance seven times over." Then the LORD put a mark on Cain so that no one who
found him would kill him. \V So Cain went out from the LORD's presence and lived
in the land of Nod, east of Eden.

\V Cain lay with his wife, and she became pregnant and gave birth to Enoch. Cain
was then building a city, and he named it after his son Enoch. \V To Enoch was
born Irad, and Irad was the father of Mehujael, and Mehujael was the father of
Methushael was the father of Lamech.

\V Lamech married two women, one named Adah and the other Zillah. \V Adah gave
birth to Jabal; he was the father of those who live in tents and raise
livestock. \V His bother's name was Jubal; he was the father of all who play the
harp and flute. \V Zillah also had a son, Tubal-Cain, who forged all kinds of
tools out of bronze and iron. Tubal-Cain's sister was Naamah.

\V Lamech said to his wives,

\begin{quotation}
"Adah and Zillah, listen to me;\\
wives of Lamech, hear my words.\\
I have killed a man for wounding me,\\
a young man for injuring me.\\
\V If Cain is avenged seven times,\\
then Lamech seventy-seven times."
\end{quotation}

\V Adam lay with his wife again, and she gave birth to a son and named him Seth,
saying, "God has granted me another child in place of Abel, since Cain killed
him." \V Seth also had a son, and he named him Enosh.

At that time men began to call on the name of the LORD.
