\T{From Adam to Noah}
\C This is the written account of Adam's line.

When God created man, he made him in the likeness of God. \V He created them
male and female and blessed them. And when they were created, he called them
"man."

\V When Adam have lived 130 years, he had a son in his own likeness, in his own
image; and he named him Seth. \V After Seth was born, Adam lived 800 years and
had other sons and daughters. \V Altogether, Adam lived 930 years, and then he
died.

\V When Seth had lived 105 years, he became the father of Enosh. \V And after he
became of the father of Enosh, Seth lived 807 years and had other sons and
daughters. \V Altogether, Seth lived 912 years, and then he died.

\V When Enosh ha lived 90 years, he became the father of Kenan. \V And after he
became the father of Kenan, Enosh lived 815 years and had other sons and
daughters. \V Altogether, Enosh lived 905 years, and the he died.

\V When Kenan ha lived 70 years, he became the father of Mahalalel. \V And after
he became the father of Mahalalel, Kenan lived 840 years and had other sons and
daughters. \V Altogether, Kenan lived 910 years, and then he died.

\V When Mahalalel ha lived 65 years, he became the father of Jared. \V And after
he became the father of Jared, Mahalalel lived 830 years and had other sons and
daughters. \V Altogether, Mahalalel lived 895 years, and then he died.

\V When Jared had lived 162 years, he became the father of Enoch. \V And after
he became the father of Enoch, Jared lived 800 years and had other sons and
daughters. \V Altogether, Jared lived 962 years, and then he died.

\V When Enoch had lived 65 years, he became the father of Methuselah. \V And
after he became the father of Methuselah, Enoch walked with God 300 years and
had other sons and daughters. \V Altogether, Enoch lived 365 years. \V Enoch
walked with God; then he was no more, because God took him away.

\V When Methuselah had lived 187 years, he became the father of Lamech. \V And
after he became the father of Lamech, Methuselah lived 782 years and had other
sons and daughters. \V Altogether, Methuselah lived 969 years, and then he died.

\V When Lamech had lived 182 years, he had a son. \V He named him Noah and said,
"He will comfort us in the labor and painful toil of our hands caused by the
ground the LORD has cursed." \V After Noah was born, Lamech lived 595 years and
had other sons and daughters. \V Altogether, Lamech lived 777 years, and then he
died.

\V After Noah was 500 years old, he became the father of Shem, Ham and Japheth.
