\T{The Flood}
\C When men began to increase in number on the earth and daughters were born to
them, \V the sons of God saw that the daughters of men were beautiful, and they
married any of them they chose. \V Then the LORD said, "My Spirit will note
contend with man forever, for he is mortal; his days will be a hundred and
twenty years."

\V The Nephilim were on the earth in those days -- and also afteward -- when the
sons of God went to the daughters of men and had children by them. They were the
heroes of old, men of renown.

\V The LORD saw how great man's wickedness on the earth had become, and that
every inclination of the thoughts of his heart was only evil all the time. \V
The LORD was grieved that he had made man on the earth, and his heart was filled
with pain. \V So the LORD said, "I will wipe mankind, whom I have created, from
the face of the earth -- men and animals, and creatures that move along the
ground, and birds of the air -- fro I am grieved that I have made them." \V But
Noah found favor in the eyes of the LORD.

\V This is the account of Noah.

Noah was a righteous man, blamelles amoung the people of his time, and he walked
with God. \V Noah had three sons: Shem, Ham and Japheth.

\V Now the earth was corrupt in God's sight and was full of violence. \V God saw
how corrupt the earth had become, for all the people on earth had corrupted
their ways. \V So God said to Noah, "I am going to put an end to all people, for
the earth if filled with violence because of them. I am surely going to destory
both them and the earth. \V So make yourself an ark of cypress wood; make rooms
in it and coat it with pitch inside and out. \V This is how you are to build it:
The ark is to be 450 feet long, 75 feet wide and 45 feet high. \V Make a roof
for it and finish the ark to within 18 inches of the top. Put a door in the side
of the ark and make lower, middle and upper decks. \V I am going to brind
floodwaters on the earth to destroy all life in it. Everything on earth will
perish. \V But I will establish my covenant with you, and you will enter the ark
-- you and your sons and your wife and your son's wives with you. \V You are to
bring into the ark two of all living creatures, male and female, to keep them
alive with you. \V Two of every kind of bird, of every kind of animal and of
every kind of creature that moves along the ground will come to you to be kept
alive. \V You are to take every kind of food that is to be eaten and store it
away as food for you and for them."

\V Noah did everything just as God commanded him.

\C The LORD then said to Noah, "Go into the ark, you and your whole family,
because I have found you righteous in this generation. \V Take with you seve of
every kind of clean animal, a male and its mate, and two of every kind of
unclean animal, a male and its mate, \V and also seven of every kind of bird,
male and female, to keep their various kinds alive throughout the earth. \V
Seven days from now I will send rain on the earth for forty days and forty
nights, and I will wipe from the face of the earth every living creature I have
made."

\V And Noah did all that the LORD commanded him.

\V Noad was six hundred years old when the floodwaters came on the earth. \V And
Noah and his sons and his wife and his son's wives entered the ark to escape the
waters of the flood. \V Pairs of clean and unclean animals, of birds and of all
creatures that move along the ground, \V male and female, came to Noah and
entered the ark, as God had commanded Noah. \V And after seven days the
floodwaters came on the earth.

\V In the six hundredth year of Noah's life, on the seventeenth day the second
month -- on that day all the springs of the great deep burst forth, and the
floodgates of the heavens were opened. \V And rain fell on the earth forty days
and forty nights.

\V On that very day Noah and his sons, Shem, Ham and Japheth, together with his
wifes and the wives of his three sons, entered the ark. \V They had with them
every wild animal according to its kind, all livestock acoording to their kinds,
every creature that moves along the ground according to its kind and every bird
according to its kind, everything with wings. \V Pairs of all creatures that
have the breath of life in them came to Noah and entered the ark. \V The animals
going in were male and female of every living thing, as God had commanded Noah.
Then the LORD shut him in.

\V For forty days the flood kept comming on the earth, and as the waters rose
and increased greatly on the earth, and the ark floated on the surface of the
water. \V They rose greatly on the earth, and all the high mountains under the
entire heavens were covered. \V The waters rose and covered the mountains to a
depth of more that twenty feet. \V Every living thing that moved on the earth
perished -- birds, livestock, wild animals, all the creatures that swarm over
the earth, and all mankind. \V Everything on dry land that had the breath of
life in its nostrils died. \V Every living thing on the face of the earth was
wiped out; men and animals and the creatures that move along the ground and the
birds of the air were wiped from the earth. Only Noah was left, and those with
him in the ark.

\V The waters flooded the earth for a hundred and fifty days.

\C But God remembered Noah and all the wild animals and the livestock that were
with him in the ark, and he sent a wind over the earth, and the waters recede.
\V Now the springs of the deep and the floodgates of the heavens had been
closed, and the rain had stopped falling from the sky. \V The water receded
steadily from the earth. At the end of the hundred and fifty days the water had
gone down, \V and on the seventeenth day of the seventh month the ark came to
rest on the mountains of Ararat. \V The waters continued to recede until the
tenth month, and on the first day of the tenth mounth the tops of the mountains
became visible.

\V After forty days Noah opened the window he had made in the ark \V and sent
out  a rave, and it kept flying back and forth until the water had dried up from
the earth. \V Then he sent out a dove to see if the water had receded from the
surface of the ground. \V But the dove could find no place to set its feet
because there was water over all the surface of the earth; so it returned to
Noah in the ark. He reached out his hand and took the dove and brought it back
to himself in the ark. \V He waited seven more days and again sent out the dove
from the ark. \V When the dove returned to him in the evening, there in its beak
was a freshly plucked olive leaf! Then Noah knew that the water had receded from
the earth. \V He waited seven more days and sent the dove out again, but this
time it did not return to him.

\V By the first day of the first month of Noah's six hundred and first year, the
water had dried up from the earth. Noah then removed the covering from the ark
and saw that the surface of the ground was dry. \V By the twenty-seventh day of
the second month the earth was completely dry.

\V Then God said to Noah, \V "Come out of the ark, you and your wife and your
sons and their wives. \V Bring out every kind of living creature that is with
you -- the birds, the animals, and all the creatures that move along the ground
-- so they can multiply on the earth and be fruitful and increase in number upon
it."

\V So Noah came out, together with his sons and his wife and his son's wives. \V
All teh animals and all the creatures that move along the ground and all the
birds -- everything that move on the earth -- came out of the ark, one kind
after another.

\V Then Noah built an altar to the LORD and, taking some of all the clean
animals and clean birds, he sacrificed burnt offerings on it. \V The LORD
smelled the pleasing aroma and said in his heart: "Never again will I curse the
ground because of man, even though every inclination of his heart is evil from
childhood. And never again will I destroy all living creatures, as I have done."

\begin{quotation}
\V "As long as the earth endures,\\
seedtime and harvest,\\
cold and heat,\\
summer and winter,\\
day and night\\
will never cease."
\end{quotation}
