\T{God's Covenant With Noah}
\C Then God blessed Noah and his sons, saying to them, "Be fruitful and increase
in number and fill the earth. \V The fear and dread of you will fall upon all
the beasts of the earth and all the birds of the air, upon every creature that
moves along the ground, and upon all the fish of the sea; they are given into
your hands. \V Everything that lives and moves will be food for you. Just as I
gave you the green plants, I now give you everything."

\V "But you must not eat meat that has its lifeblood still in it. \V And for
your lifeblood I will surely demand and accounting. I will demand and accounting
from every animal. And from each man, too, I will demand and accounting for the
life of his fellow man."

\begin{quotation}
\V "Whoever sheds the blood of man.\\
by man shall his blood be shed;\\
for in the image of God\\
has God made man."
\end{quotation}

\V "As for you, be fruitful and increase in number; multiply on the earth and
increase upon it."

\V Then God said to Noah and to his sons with him: \V "I now establish my
covenant with you and with your descendants after you \V and with every living
creature that was with you -- the birds, the livestock and all the wild animals,
all those that came out of the ark with you -- every living creature on earth.
\V I establish my covernant with you: Never again will all life be cut off by
the waters of a flood; never again will there be a flood to destroy the earth."

\V And God said, "This is the sign of the covenant I am making between me and
you and every living creature with you, a covenant for all generations to come:
\V I have set my rainbow in the clouds, and it will be the sign of the covenant
between me and the earth. \V Whenever I bring clouds over the earth and the
raibow appears in the clouds, \V I Will remember my covenant between me and you
and all living creatures of every kind. Never again will the waters become a
flood to destroy all life. \V Whenever the rainbow appears in the clouds, I will
see it and remember the everlasting covenant between God and all living
creatures of every kind on the earth."

\V So God said to Noah, "This is the sign of the covenant I have established
between me and all life on the earth."
